The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-11-30 manuscript/manuscript.qmd
Update early figures (fixes #21)

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China under the 2017 ONGO law, either as formal Registered Organizations 
#|   (ROs) or by undertaking specific Temporary Activities (TAs)"
ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Keep programming within approved scope",
    "Submit annual work plans to PSU and Public Security Bureau",
    "Submit annual reports to PSU and Public Security Bureau"
  ),
  type = "Registered organization (RO)"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

ta_nodes <- tibble(
  step = c(
    "Find an eligible Chinese partner to file paperwork",
    "Obtain PSU approval",
    "Channel money through partner’s bank",
    "Keep programming within approved scope",
    "Finish work within a year",
    "Submit final project report to Public Security Bureau"
  ),
  type = "Temporary activities (TA)"
)
ta_edges <- tibble(from = 1:5, to = 2:6)
ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)

@@

```{r fig-theory, fig.width=6, fig.height=2}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational flexibility: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 1, 0, FALSE,
  2,   "Operational flexibility", 3, 0, TRUE,
  3,   "Local focus", 2, 1, FALSE,
  4,   "Government preferences", 2, -1, FALSE
)

>>>>

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China under the 2017 ONGO law, either as formal Registered Organizations 
#|   (ROs) or by undertaking specific Temporary Activities (TAs)"

ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Keep programming within approved scope",
    "Submit annual work plans to PSU and Public Security Bureau",
    "Submit annual reports to PSU and Public Security Bureau"
  ),
  type = "Registered organization (RO)"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

ta_nodes <- tibble(
  step = c(
    "Find an eligible Chinese partner to file paperwork",
    "File activity information with Public Security Bureau",
    "Keep programming within approved scope",
    "Finish work within a year",
    "Submit final project report to Public Security Bureau"
  ),
  type = "Temporary activities (TA)"
)
ta_edges <- tibble(from = 1:4, to = 2:5)
ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)

@@

```{r fig-theory, fig.width=6, fig.height=2}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 1, 0, FALSE,
  2,   "Operational space", 3, 0, TRUE,
  3,   "Local focus", 2, 1, FALSE,
  4,   "Government preferences", 2, -1, FALSE
)
